PANCHANGE_analysis

### 2020-12-18 PANCHANGE_analysis.Rmd
added PCl violin plot

@@

### add a single "other ethnicity individual" as a jitter for NBR so this category remains included wihout adding explanation.
```{r add jitter "other" for NBR other ethnicity so this cat is available for plotting}

dat.retro.nbr$Ethnicity_collapsed[801] <- "Other"  #this person was an NA
dat.retro.nbr$Ethnicity_collapsed[998] <- "Other"  #this person was an NA

>>>>

```{r pcl.sum violin plot sample}
dat.long.pcl.sum %>%
  filter(Time_point != "retro") %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD and EDGI",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>% 
  mutate(Time_point_renamed = fct_recode(Time_point,
                                         "Prepandemic" = "prepan",
                                         "Baseline" = "base")
  ) %>%
  mutate(Time_point_reordered = fct_relevel(Time_point_renamed,
                                            "Baseline",
                                            "Prepandemic")
  ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = pcl.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 21, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
  ) +
  geom_point(
    aes(
      y = pcl.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
  #  geom_boxplot(
  #    width = .1,
  #    guides = FALSE,
  #    outlier.shape = NA,
  #    alpha = 0.5) +
  stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x),
               fun.ymax = function(x) mean(x) + sd(x),
               geom = "pointrange"
  ) +
  labs(
    y = "PCL scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Baseline")
  ) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Baseline"),
    guide = "none") +
    facet_wrap(facets = vars(sample),
             nrow = 4
  ) +
  coord_flip()
```

@@

### add a single "other ethnicity individual" as a jitter for NBR so this category remains included wihout adding explanation.
```{r add jitter "other" for NBR other ethnicity so this cat is available for plotting}
dat.retro.nbr$Ethnicity_collapsed[586] <- "Other"  #this person was an NA
dat.retro.nbr$Ethnicity_collapsed[856] <- "Other"  #this person was an NA
dat.retro.nbr$Ethnicity_collapsed[871] <- "Other"  #this person was an NA
